\documentclass[12pt]{article}
	\title {BRIEF HISTORY OF FIVE PROGRAMMING LANGUAGES}
\author{ILOBA MICHAEL}
\begin{document}
	\maketitle
	\newpage
	\section{PHP}

	\begin{itemize}
		

	\item \textbf{PHP} WHICH MEANS HYPERTEXT PRE-PROCESSOR IS AN ALL-PURPOSE SCRIPTING LANGUAGE USED FOR MAKING DYNAMIC WEBPAGES AND WEB APPLICATIONS. IN 1994, \textbf{PHP} WAS MADE BY RASMUS LERDORF, A CANADIAN PROGRAMMER AND BEFORE RELEASING IT TO THE WORLD IN 1995, HE USED IT TO KNOW THOSE WHO WERE LOOKING AT HIS RESUME ONLINE. \textbf{PHP} WAS KNOWN AS PERSONAL HOME PAGE IN THE PAST.
	
	\item \textbf{PHP} CAN BE APPLIED IN GUI-BASED APPLICATIONS, WEB PAGES, WEB-BASED APPLICATIONS, E-COMMERCE ETC.

	\item FACEBOOK, WIKIPEDIA, SLACK AND TUMBLR ARE SOME OF THE APPLICATIONS THAT USE \textbf{PHP}.

	\item THERE ARE SEVERAL \textbf{PHP} IDEs (INTEGRATED DEVELOPMENT ENVIRONMENT) LIKE DREAM WEAVER, KOMODO AND NOTEPAD++ THAT GIVE SMART CODE COMPLETION AND CORRECT ERRORS QUICKLY.
	PROGRAMMING LANGUAGES SUCH AS RUBY, PYTHON AND GOLANG ARE RELATED TO PHP AND CAN BE USED AS AN ALTERNATIVE
	
		\newpage
	\section{C SHARP}
\item	\textbf{C SHARP} IS AN OBJECT-ORIENTED PROGRAMMING LANGUAGE DEVELOPED BY A DANISH SOFTWARE ENGINNER ANDERS HEJLSBERG FROM MICROSOFT. \textbf{C SHARP} WAS DEVELOPED IN 2000, BUT IT WAS APPROVED IN 2002 BY ECMA AS AN INTERNATIONAL STANDARD.
	\item	\textbf{C SHARP} IS USED IN THE DEVELOPMENT OF WEBSITE, WINDOWS APPLICATIONS AND GAMES.
	\item
	PAINT.NET, KEEPASS AND OPEN DENTAL ARE EXAMPLES OF APPLICATIONS DEVELOPED BY \textbf{C SHARP}.
	\item
	SOME \textbf{C SHARP} IDE INCLUDES VS CODE, KITE AND SLICKEDIT.
	\item
	C++, JAVA AND JAVASCRIPT ARE PROGRAMMING LANGAGES THAT ARE RELATED TO \textbf{C SHARP}.
	\newpage
	\section{JS}
	\item
	\textbf{JS }WHICH IS ALSO KNOWK AS \textbf{JAVASCRIPT} IS A HIGH-LEVEL SCRIPTING PROGRAMMING LANGUAGE AND IT IS ONE OF THE MOST POPULAR PROGRAMMING LANGUAGE.IT IS USED TOGETHER WITH HTML AND CSS TO MAKE WEBSITE. IT MAKES THE WEBSITE FUNCTIONAL. IN 1995, BRENDAN EICH DEVELOPED \textbf{JAVASCRIPT} FOR NETSCAPE 2. IT WAS FIRST CALLED MOCHA THEN LIVE SCRIPT THEN LATER \textbf{JAVASCRIPT}.
	\item
	\textbf{JAVASCRIPT} IS MAINLY USED FOR MAKING DYNAMIC WEBPAGES.
	\item
	FAMOUS APPS LIKE NETFLIX, FACEBOOK AND UBER WERE MADE USING \textbf{JAVASCRIPT}
	\item
	ATOM AND VISUAL STUDIO CODE ARE SOME OF THE BEST IDEs FOR \textbf{JAVASCRIPT}
	\item
	DART, OPAL AND ELM ARE PROGRAMMING LANGUAGE THAT ARE SIMILAR TO \textbf{JAVASCRIPT} AND CAN BE USED AS AN ALTERNATIVE TO \textbf{JAVASCRIPT}
	 
	\newpage
	\section{PYTHON}
	\item
	\textbf{PYTHON}, A HIGH LEVEL PROGRAMMING LANGUAGE, WAS FORMULATED BY GUIDO VAN ROSSUM FROM THE NETHERLANDS IN THE LATE 1980s. ITS APPLICATION STARTED IN 1989.
	\item
	\textbf{PYTHON} CAN BE APPLIED IN WEB DEVELOPED WITH \textbf{PYTHON} INCLUDE PINTEREST, SPOTIFY , UBER AND DROPBOX.
	\item
	SOME APPLICATIONS DEVELOPED WITH \textbf{PYTHON} INCLUDE PINTEREST, SPOTIFY, UBER AND DROPBOX. 
	\item
	SOME IDEs FOR \textbf{PYTHON} INCLUDE ATOM INCLUDE ATOM, VS (VISUAL STUDIO) CODE, JUPYTER AND PYDEV.
	\item
	\textbf{PYTHON} IS USUALLY COMPARED TO RUBY AND JAVA BECAUSE THE FORMER AND \textbf{PYTHON} HAVE SIMILAR USE CASES WHILE THE LATTER LIKE \textbf{PYTHON} IS OBJECT-ORIENTED
	\newpage
	\section{BASIC}
	\item
	\textbf{BASIC} WHICH MEANS BEGINNER'S ALL-PURPOSE SYMBOLIC INSTRUCTION CODE BELONGS TO THE FAMILY OF ALL-PURPOSE PROGRAMMING LANGUAGES. THE LANGUAGE STARTED AT DARTMOUTH COLLEGE AND WAS DEVELOPED BY JOHN G. KEMENEY AND THOMAS E. KURTZ IN 1964. \textbf{BASIC} IS A HIGH LEVEL PROGRAMMING LANGUAGE THAT WAS CREATED TO MAKE STUDENTS IN OTHER FIELDS TO USE COMPUTERS
	\item
	TEACHERS MAKE USE OF \textbf{BASIC} PROGRAMMING LANGUAGE TO TEACH THE INTRODUCTORY PART OF PROGRAMMING.
	\item
	VINTAGEBASIC AND MICROSOFT VISUAL CODE ARE SOME IDEs FOR \textbf{BASIC} PROGRAMMING LANGUAGE.
	\item
	SOME OF THE PROGRAMMING LANGUAGES THAT ARE SIMILAR TO \textbf{BASIC} INCLUDE PYTHON AND RUBY
		\end{itemize}

	
\end{document}